Modelling the Trojan Asteroids

### 2020-04-23 Report/draft1.tex
final 2d_perturbations

Horseshoe taylor \cite{Taylor1981}

@@

The "tadpole" orbit in Figure \ref{fig:orbit_rad} consists of two oscillating components, as described in Section \ref{lagrange}. The short period, measured at $11.85 \pm 0.61$ years, is in agreement with  planetary orbital period as expected; meanwhile the long period is measured to be $148 \pm 5$ years, in agreement with the analytical value of $144$ years.

For larger perturbations, horseshoe orbits may also be observed...

@@

>>>>

@@

The "tadpole" orbit in Figure \ref{fig:orbit_rad} consists of two oscillating components, as described in Section \ref{lagrange}. The short period, measured at $11.85 \pm 0.61$ years, is in excellent agreement with  planetary orbital period as expected; meanwhile the long period is measured to be $148 \pm 5$ years, consistent with the analytical value of $144$ years.

For a narrow range of larger perturbations, stable horseshoe orbits encompassing both Lagrange points may also be observed as depicted in Figure \ref{fig:horseshoe}. This has a full period of $353$ years, in agreement with Taylor et al.'s numerical result of $358 \pm 7$ years \cite{Taylor1981}.

%smooth families of horseshoe-shaped longperiodic orbits for alpha2 > 1. Smooth, because they are restricted to shallow resonance, where the evolution of the epicyclic cusps and loops cannot be seen. - according to taylor, but havn't found smooth orbits here

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/horseshoe}
	\caption{Horseshoe and tadpole orbits in the rotating frame, from radial perturbations of 0.07 and 0.01 AU respectively, over 30 orbital periods.}
	\label{fig:horseshoe}
\end{figure}

@@

\subsection{Variation of Planetary Mass}
